\chapter{Introduction} % Main chapter title

\label{ch:intro}

\lhead{Chapter 1. \emph{Introduction}}

\section{Motive}
There is a growing demand for advanced cockpit electronic systems as a result of the automotive industry's ongoing shift towards electric mobility. These technologies are essential for enabling comprehensive vehicle component monitoring and for providing the occupants with a clear, comprehensive overview of the current state and overall health of the vehicle. \\
The battery of the car is by far the most important of the crucial factors that need constant monitoring. This is particularly important for battery packs made mostly of Li-ion substrates because of the potential for severe, potentially dangerous consequences if their health and charge states are not strictly monitored. \\
Given these factors, Analog Devices Inc. provides a wBMS solution that is simple to integrate into the automotive setting. Notably, such technology is finding support with Tier 1 auto suppliers for example Stellantis and Visteon, who work closely with OEMs for example Tata, Honda, and Tesla. End-to-end solutions that enable users to thoroughly monitor various aspects of battery health are finally provided as the result of these collaborations.

\section{Contribution to the project}
This project has provided the chance to significantly advance the implementation and verification of functional safety, particularly at the level of battery monitoring sensors, the exact details of which will be discussed in the later sections. 